Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-23 paper/paper.tex
pass

\author{
\IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
\IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
\{isol2,damorim\}@cin.ufpe.br}
}

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). As the same engine is used, test outcomes are
expected to be identical. Mozilla uses this approach since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
popularized to similar extent. One possible reason is that it is still
not practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Table~\ref{tab:false-positives}). Recently, Patra and
Pradel~\cite{patra2016learning} explored the idea. They proposed a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. Their main contribution is analytical whereas our main
contribution is empirical--goal is to evaluate ability and cost of
simple diversity-aware approaches to find bugs in \js\ engines.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. In contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace subtrees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew.

@@

\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment we analyzed each failure observed in a test
execution. A developer with experience in \js\ analyzed each files in
separate and classified the failure as potentially fault-revealing or
not (\ie{}, a false positive). The co-authors supervised the
classification process as to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug
(or re-classified the failure as a false alarm).

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making the test to pass only in \chakra\ for
that test. As another example, some tests from \Fix{Y} use the
implementation-dependent description message\Mar{what is the name of
  the property?} encapsulated in an \CodeIn{Error} object in
assertions. As such, those tests fail in all engines but
\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind manifest because the engine
that runs the test does not optimize the code as the original engine
and that has an effect in the test outcome.  The test may fail to
finish at the specified time budget or it exceeds the memory
budget. For example, a test case from the \jsc{} suite defines a
function with a tail-call recursion. The test fails in all engines but
\jsc{}, which implements tail-call optimization, which enables the
test to finish execution fast. \textbf{Not implemented.} False
positives of this kind manifest when a test fails because it covers a
function that is part of the official spec, but is not implemented in
the target engine yet. For example, at the time of writing, \chakra{}
does not implement by default various properties from the
\mcodeid{Symbol} object. These properties are only available
activating the ES6 experimental mode with the flag
\CodeIn{-ES6Experimental}. \Mar{revise this.}\textbf{Unknown.} This
category includes the cases we were unable to confidently diagnose the
failure but we suspected it was a false alarm.

\begin{figure}[h]
  \centering
  \subfloat[\label{fig:falsepositives}False Positives]{%
    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
  }
  \label{1a}\hfill
  \subfloat[\label{fig:truepositives}True Positives]{%
    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
  }
  \label{1b}\\
  \caption{\label{fig:piecharts-transplantation}False and True positives.}
\end{figure}

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
distribution of false and true positives in this experiment. The
piechart at the top shows false alarms. The absolute number of tests
in each category is shown in parentheses to the right-side of each
slice label naming the source of false positive.  We observed that
``Unknown'' and ``Undefined'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   19 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
   20 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
   21 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
   22 & 8/22  & \jsc{} & New &  & - & \smonkey{}\\
   \midrule
    \multirow{3}{*}{23}  & 
    \multirow{3}{*}{8/22} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
    &  &
    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
    &  &
    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
   \midrule
   24 & 8/23  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the bug report
entry in the bug tracking system (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are rare. Considering the bugs
confirmed by developers, \chakra{} was the engine with the highest
number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
remaining engines, \veight{} developers confirmed \Fix{one} bug we
reported. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.\Fix{falta add test262}}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of three new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. \Igor{devemos remover isso da 
etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
The source ``Upcoming Feature''
indicates that the test fails because it uses a feature that is
available in the original engine, but it is still not standard, and
the target engine does not support that feature}. For example,
\Fix{provide concrete example}. \Fix{explain error message mismatch}

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined Behavior & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    * Invalid Input & 10 & - \\    
    % * Upcoming Feature & - & - \\
    * Error Message Mismatch & 3 & - \\        
    \bottomrule     
  \end{tabular}
\end{table}

@@

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in \chakra{} due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
function test() {
  return typeof String.prototype.repeat === "function"
    && "foo".repeat(657604378) === "foofoofoo";
}
if (!test())
  throw new Error("Test failed");
  \end{lstlisting}
  \normalsize
  \caption{Warning captured as HI priority.}
  \label{fig:hi-priority}
  \end{figure}

>>>>

%% \author{
%% \IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
%% \IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
%% \{isol2,damorim\}@cin.ufpe.br}
%% }

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). As the same engine is used in this
scenario, test outcomes are expected to be identical. The Mozilla team
uses this approach since 2002; they have been able to find over 270
bugs since then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
very popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}).

%% Recently, Patra and
%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
%% find cross-browser HTML+JS discrepancies. The main difference of our
%% work to theirs is in goal; our goal is to evaluate ability and cost of
%% simple diversity-aware approaches to find bugs in \js\ engines.

%% Their main contribution was
%% analytical whereas our main contribution is empirical--

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines analyzed.}
  \begin{tabular}{cccrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace subtrees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew.

@@

\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment, a developer with experience in \js\ analyzed each
test file that reveals failure in a given engine and classified that
file as potentially fault-revealing or not. The co-authors supervised
the classification process to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug,
if confirmed, or re-classified the failure as a false alarm.

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making the test to pass only in \chakra\ for
that test. As another example, some tests from \Fix{Y} use the
implementation-dependent description message\Mar{what is the name of
  the property?} encapsulated in an \CodeIn{Error} object in
assertions. As such, those tests fail in all engines but
\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind manifest because the engine
that runs the test does not optimize the code as the original engine
and that has an effect in the test outcome.  The test may fail to
finish at the specified time budget or it exceeds the memory
budget. For example, a test case from the \jsc{} suite defines a
function with a tail-call recursion. The test fails in all engines but
\jsc{}, which implements tail-call optimization, which enables the
test to finish execution fast. \textbf{Not implemented.} False
positives of this kind manifest when a test fails because it covers a
function that is part of the official spec, but is not implemented in
the target engine yet. For example, at the time of writing, \chakra{}
does not implement by default various properties from the
\mcodeid{Symbol} object. These properties are only available
activating the ES6 experimental mode with the flag
\CodeIn{-ES6Experimental}. \Mar{pela explicacao de
  ``compile-in-all'', isto nao faz sentido.$\rightarrow$} \textbf{Non-Standanrd Element.} This kind
corresponds to the cases the test case relies on some non-standard
function or property of a standard object. \Mar{revise this.$\rightarrow$}\textbf{Unknown.} This
category includes the cases we were unable to confidently diagnose the
failure but we suspected it was a false alarm.

%% \begin{figure}[h]
%%   \centering
%%   \subfloat[\label{fig:falsepositives}False Positives]{%
%%     \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
%%   }
%%   \label{1a}\hfill
%%   \subfloat[\label{fig:truepositives}True Positives]{%
%%     \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
%%   }
%%   \label{1b}\\
%%   \caption{\label{fig:piecharts-transplantation}False and True positives.}
%% \end{figure}

\begin{table}[h!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
    & Timeout/OME & 13 \\
    & Not Implemented & 21 \\
    & Non-Standard Element & \Fix{132} \\
    & Unknown & \Fix{-} \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

%%  The piechart at the top
%% shows false alarms. The absolute number of tests in each category is
%% shown in parentheses to the right-side of each slice label naming the
%% source of false positive.

\begin{table}[t!]
\setlength{\tabcolsep}{5pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{rcccccc}
    \toprule Issue\#\Comment{    & Date} & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  \Comment{& 4/18  }& JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  \Comment{& 4/23 }& \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\

   3  \Comment{& 4/29 }& \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}}
    & 2 & \smonkey{} \\

    \multirow{2}{*}{4}\Comment{& \multirow{2}{*}{4/29}} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &\Comment{  &}
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   5 \Comment{& 5/02  }& \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 \Comment{& 5/17  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 \Comment{& 5/21  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 \Comment{& 6/28  }& \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 \Comment{& 7/10  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 \Comment{& 7/18  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 \Comment{& 8/08  }& \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 \Comment{& 8/08  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   19 \Comment{& 8/16  }& \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
   20 \Comment{& 8/22  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
   21 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
   22 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{?????????????????????}{???}} & - & \smonkey{}\\
%   \midrule
    \multirow{3}{*}{23}\Comment{& 
    \multirow{3}{*}{8/22}} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
    &  \Comment{&}
    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
    &  \Comment{&}
    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
%   \midrule
   24 \Comment{& 8/23  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',} column ``Engine'' shows the
affected engine, column ``Status'' indicates the status of the bug
report at the time of the writing (\eg{},``New'', ``Rejected'',
``Confirmed'', ``Fixed''). The status string appear in bold face for
status ``Confirmed'' or higher (\ie{}, ``Assigned'' or ``Fixed'').
Column ``Url'' shows the URL (de-anonymized upon request) for the bug report entry in the
corresponding bug-tracking system, column ``Severity''
shows the severity level for confirmed bugs, and, finally, column
``Suite'' shows the name of the engine that originated the
test. Note that bug reports \#4 and \#23 afected multiple engines.

Considering severity levels, it is important to note that \jsc{}
uses five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are rare. Considering the bugs
confirmed by developers, \chakra{} was the engine with the highest
number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
remaining engines, \veight{} developers confirmed \Fix{one} bug we
reported. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018.

@@

\begin{table}[h]
  \setlength{\tabcolsep}{5pt}
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.\Fix{falta add test262}}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of three new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications.

%% \Igor{devemos remover isso da 
%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
%% The source ``Upcoming Feature''
%% indicates that the test fails because it uses a feature that is
%% available in the original engine, but it is still not standard, and
%% the target engine does not support that feature}. For example,
%% \Fix{provide concrete example}. \Fix{explain error message mismatch}

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 18 & - \\
    & Timeout/OME & 23 & - \\
    & Not Implemented & 19 & - \\
    & * Invalid Input & 10 & - \\    
    & * Error Message Mismatch & 3 & - \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & - \\
    & Bug & - \\
    \bottomrule     
  \end{tabular}
\end{table}

@@

An example of a warning from the \hi{} group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in \chakra{} due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
function test() {
  return typeof String.prototype.repeat === "function"
    && "foo".repeat(657604378) === "foofoofoo";
}
if (!test())
  throw new Error("Test failed");
  \end{lstlisting}
  \normalsize
  \caption{Warning captured as \hi{} priority.}
  \label{fig:hi-priority}
  \end{figure}
